---
title: "Computational Modeling - Assignment 1"
author: "Riccardo Fusaroli"
date: "07/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## In this assignment we learn how to assess rates from a binomial distribution, using the case of assessing your teachers' knowledge of CogSci

N.B. this markdown has 2 parts as it spans 2 weeks of teaching

### First part

You want to assess your teachers' knowledge of cognitive science. "These guys are a bunch of drama(turgist) queens, mindless philosophers, chattering communication people and Russian spies. Do they really know CogSci?", you think.

To keep things simple (your teachers should not be faced with too complicated things):
- You created a pool of equally challenging questions on CogSci
- Each question can be answered correctly or not (we don't allow partially correct answers, to make our life simpler).
- Knowledge of CogSci can be measured on a scale from 0 (negative knowledge, all answers wrong) through 0.5 (random chance) to 1 (awesome CogSci superpowers)

This is the data:
- Riccardo: 3 correct answers out of 6 questions
- Kristian: 2 correct answers out of 2 questions (then he gets bored)
- Daina: 160 correct answers out of 198 questions (Daina never gets bored)
- Mikkel: 66 correct answers out of 132 questions

Questions:

1. What's Riccardo's estimated knowledge of CogSci? What is the probability he knows more than chance (0.5) [try figuring this out. if you can't peek into chapters 3.1 and 3.2 and/or the slides]?

- First implement a grid approximation (hint check paragraph 2.4.1!) with a uniform prior, calculate the posterior and plot the results

```{r}
# load packages
library(tidyverse)
library(rethinking)
library(ggplot2)


## Grid approximation

# creating an object called dens = 20 (dens is the steps between 0-1, and now has 20 steps)
dens <- 20
p_grid <- seq(from = 0, to = 1, length.out = dens)

# define the prior
prior <- rep(1, dens) # flat
prior1 <- ifelse(p_grid < 0.5, 0, 1) # It is unlikely that Riccardo answers less than half the questions correctly (below 0.5) because he is a teacher of cogsci, therefore we want the prior to be 0 in such case.
prior2 <- dnorm(p_grid, 0.5, 0.1) # the prior is a normal distribution centered at chance (0.5 chance of answering all the questions correctly)

# Test the prior (1e4 = 10000)
dens(rbinom(1e4, 6, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
likelihood <- dbinom(3, size = 6, prob = p_grid)
# 3 is the number of correct answers, 6 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
unstd.posterior <- likelihood * prior
unstd.posterior1 <- likelihood * prior1
unstd.posterior2 <- likelihood * prior2
# Standardize the posterior (so it sums to 1)
posterior <- unstd.posterior/sum(unstd.posterior)
posterior1 <- unstd.posterior1/sum(unstd.posterior1)
posterior2 <- unstd.posterior2/sum(unstd.posterior2)

# make dataframes to draw plots 
d <- data.frame(grid= p_grid, posterior = posterior, prior = prior, likelihood = likelihood)
d1 <- data.frame(grid= p_grid, posterior = posterior1, prior = prior1, likelihood = likelihood)
d2 <- data.frame(grid= p_grid, posterior = posterior2, prior = prior2, likelihood = likelihood)

# Draw plots ()
ggplot(d, aes(grid, posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior/dens), colour='red') + xlab("Knowledge of CogSci - flat prior") + ylab("posterior probability")

ggplot(d1, aes(grid, posterior1)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior1/dens), colour='red') + xlab("Knowledge of CogSci - optimistic prior") + ylab("posterior probability")

ggplot(d2, aes(grid, posterior2)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior2/dens), colour='red') + xlab("Knowledge of CogSci - centered prior") + ylab("posterior probability")

```


- Then implement a quadratic approximation (hint check paragraph 2.4.2!).
- N.B. for the rest of the exercise just keep using the grid approximation (we'll move to quadratic approximations in two classes)

```{r}

# quadratic approximation:

Ric.qa <- quap(
  alist(
    C ~ dbinom( C+W ,p) , # binomial likelihood - C=correct / W=Wrong
    p ~ dunif(0,1) # uniform prior
  ) ,
  data=list(C=3,W=3) )
# display summary of quadratic approximation
precis( Ric.qa ) # precis presents a brief summary of the quadratic approximation

# analytical calculation
C <- 3
W <- 3
curve( dbeta( x , C+1 , W+1 ) , from=0 , to=1 )
# quadratic approximation
curve( dnorm( x , 0.5 , 0.2 ) , lty=2 , add=TRUE )


```
I am not sure I understand this fully.



 1) The probability that Riccardo knows more than chance (0.5):

```{r}
# add up posterior probability where p > 0.5
sum( posterior[ p_grid > 0.5 ] )
sum( posterior1[ p_grid > 0.5 ] )
sum( posterior2[ p_grid > 0.5 ] )
```
Answer: This differs with the changing priors. For a flat and mean-centered prior, the probability that Riccardo knows more than chance is 0.5 (50%), but for the optimistic prior, the probability is 1 (100%). This may be because we have already defined through the prior, that the probability of Riccardo knowing less than chance is 0. 





2. Estimate all the teachers' knowledge of CogSci. Who's best? Use grid approximation. Comment on the posteriors of Riccardo and Mikkel. 
```{r}

## Following the same code. I am using all three priors on all teachers to compare.

# KRISTIAN


# Test the prior
dens(rbinom(1e4, 2, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
Klikelihood <- dbinom(2, size = 2, prob = p_grid)
# 2 is the number of correct answers, 2 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
Kunstd.posterior <- Klikelihood * prior
Kunstd.posterior1 <- Klikelihood * prior1
Kunstd.posterior2 <- Klikelihood * prior2
# Standardize the posterior (so it sums to 1)
Kposterior <- Kunstd.posterior/sum(Kunstd.posterior)
Kposterior1 <- Kunstd.posterior1/sum(Kunstd.posterior1)
Kposterior2 <- Kunstd.posterior2/sum(Kunstd.posterior2)

# make dataframes to draw plots 
Kd <- data.frame(grid= p_grid, posterior = Kposterior, prior = prior, likelihood = Klikelihood)
Kd1 <- data.frame(grid= p_grid, posterior = Kposterior1, prior = prior1, likelihood = Klikelihood)
Kd2 <- data.frame(grid= p_grid, posterior = Kposterior2, prior = prior2, likelihood = Klikelihood)



```


```{r}
# DAINA



# Test the prior
dens(rbinom(1e4, 198, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
Dlikelihood <- dbinom(160, size = 198, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
Dunstd.posterior <- Dlikelihood * prior
Dunstd.posterior1 <- Dlikelihood * prior1
Dunstd.posterior2 <- Dlikelihood * prior2

# Standardize the posterior (so it sums to 1)
Dposterior <- Dunstd.posterior/sum(Dunstd.posterior)
Dposterior1 <- Dunstd.posterior1/sum(Dunstd.posterior1)
Dposterior2 <- Dunstd.posterior2/sum(Dunstd.posterior2)

# make dataframes to draw plots 
Dd <- data.frame(grid= p_grid, posterior = Dposterior, prior = prior, likelihood = Dlikelihood)
Dd1 <- data.frame(grid= p_grid, posterior = Dposterior1, prior = prior1, likelihood = Dlikelihood)
Dd2 <- data.frame(grid= p_grid, posterior = Dposterior2, prior = prior2, likelihood = Dlikelihood)


```

```{r}
#MIKKEL


# Test the prior
dens(rbinom(1e4, 132, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
Mlikelihood <- dbinom(66, size = 132, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
Munstd.posterior <- Mlikelihood * prior
Munstd.posterior1 <- Mlikelihood * prior1
Munstd.posterior2 <- Mlikelihood * prior2

# Standardize the posterior (so it sums to 1)
Mposterior <- Munstd.posterior/sum(Munstd.posterior)
Mposterior1 <- Munstd.posterior1/sum(Munstd.posterior1)
Mposterior2 <- Munstd.posterior2/sum(Munstd.posterior2)

# make dataframes to draw plots 
Md <- data.frame(grid= p_grid, posterior = Mposterior, prior = prior, likelihood = Mlikelihood)

Md1 <- data.frame(grid= p_grid, posterior = Mposterior1, prior = prior1, likelihood = Mlikelihood)

Md2 <- data.frame(grid= p_grid, posterior = Mposterior2, prior = prior2, likelihood = Mlikelihood)

```

Which teacher is best?
```{r}
# Add up posterior probability where p > 0.5 to find the probability of the teacher knowing more than chance (0.5)

# Riccardo
sum( posterior[ p_grid > 0.5 ] )
sum( posterior2[ p_grid > 0.5 ] )

# Kristian
sum( Kposterior[ p_grid > 0.5 ] )
sum( Kposterior2[ p_grid > 0.5 ] )

# Daina
sum( Dposterior[ p_grid > 0.5 ] )
sum( Dposterior2[ p_grid > 0.5 ] )

# Mikkel
sum( Mposterior[ p_grid > 0.5 ] )
sum( Mposterior2[ p_grid > 0.5 ] )

```
The probability of Daina knowing more than chance is 1, regardless of the prior. Kristian is also showing higher probability of knowing more than chance, as with the flat prior, the probability of Kristian knowing more than chance is 88% and with a centered prior, it is 65%.

Riccardo and Mikkel show the same results; there is a 50% probability that they know more than chance, with both the flat prior and the centered prior. This may be because the proportion of correct answers to incorrect answers is the same (3/6 - 66/132), they both answered correctly on half of the questions. 



2a. Produce plots of the prior, and posterior for each teacher.

```{r}
# Riccardo:
ggplot(d, aes(grid, posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")

ggplot(d1, aes(grid, posterior1)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior1/dens), colour='red') + xlab("Knowledge of CogSci - optimistic prior") + ylab("posterior probability")

ggplot(d2, aes(grid, posterior2)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior2/dens), colour='red') + xlab("Knowledge of CogSci - centered prior") + ylab("posterior probability")


# Kristian: 
ggplot(Kd, aes(grid, Kposterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior/dens), colour='red') + xlab("Knowledge of CogSci - flat prior") + ylab("posterior probability")

ggplot(Kd1, aes(grid, Kposterior1)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior1/dens), colour='red') + xlab("Knowledge of CogSci - optimistic prior") + ylab("posterior probability")

ggplot(Kd2, aes(grid, Kposterior2)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior2/dens), colour='red') + xlab("Knowledge of CogSci - centered prior") + ylab("posterior probability")



# Daina:
ggplot(Dd, aes(grid, Dposterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")

ggplot(Dd1, aes(grid, Dposterior1)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior1/dens), colour='red') + xlab("Knowledge of CogSci - optimistic prior") + ylab("posterior probability")

ggplot(Dd2, aes(grid, Dposterior2)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior2/dens), colour='red') + xlab("Knowledge of CogSci - centered prior") + ylab("posterior probability")



# Mikkel:
ggplot(Md, aes(grid, Mposterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")

ggplot(Md1, aes(grid, Mposterior1)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior1/dens), colour='red') + xlab("Knowledge of CogSci - optimistic prior") + ylab("posterior probability")

ggplot(Md2, aes(grid, Mposterior2)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior2/dens), colour='red') + xlab("Knowledge of CogSci - centered prior") + ylab("posterior probability")

```

3. Change the prior. Given your teachers have all CogSci jobs, you should start with a higher appreciation of their knowledge: the prior is a normal distribution with a mean of 0.8 and a standard deviation of 0.2. Do the results change (and if so how)?

```{r}
# Riccardo:

# define the prior
prior.3 <- dnorm(p_grid, 0.8, 0.2) # centered at chance?

# Test the prior
dens(rbinom(1e4, 6, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
likelihood.3 <- dbinom(3, size = 6, prob = p_grid)

# Compute the posterior (unstd = unstandardized)
unstd.posterior.3 <- likelihood.3 * prior.3

# Standardize the posterior (so it sums to 1)
posterior.3 <- unstd.posterior.3/sum(unstd.posterior.3)

# make dataframes to draw plots 
d.3 <- data.frame(grid= p_grid, posterior = posterior.3, prior = prior.3, likelihood = likelihood.3)




# KRISTIAN


# Test the prior
dens(rbinom(1e4, 2, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
likelihood.3k <- dbinom(2, size = 2, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
unstd.posterior.3k <- likelihood.3k * prior.3

# Standardize the posterior (so it sums to 1)
posterior.3k <- unstd.posterior.3k/sum(unstd.posterior.3k)


# make dataframes to draw plots 
d.3k <- data.frame(grid= p_grid, posterior = posterior.3k, prior = prior.3, likelihood = likelihood.3k)




# DAINA

# Test the prior
dens(rbinom(1e4, 198, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
likelihood.3d <- dbinom(160, size = 198, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
unstd.posterior.3d <- likelihood.3d * prior.3

# Standardize the posterior (so it sums to 1)
posterior.3d <- unstd.posterior.3d/sum(unstd.posterior.3d)


# make dataframes to draw plots 
d.3d <- data.frame(grid= p_grid, posterior = posterior.3d, prior = prior.3, likelihood = likelihood.3d)




# Mikkel

# Test the prior
dens(rbinom(1e4, 132, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
likelihood.3m <- dbinom(66, size = 132, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
unstd.posterior.3m <- likelihood.3m * prior.3

# Standardize the posterior (so it sums to 1)
posterior.3m <- unstd.posterior.3m/sum(unstd.posterior.3m)


# make dataframes to draw plots 
d.3m <- data.frame(grid= p_grid, posterior = posterior.3m, prior = prior.3, likelihood = likelihood.3m)

```

3a. Produce plots of the prior and posterior for each teacher.
```{r}

# Riccardo:
ggplot(d.3, aes(grid, posterior.3)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior.3/dens), colour='red') + xlab("Knowledge of CogSci - prior.3 Riccardo") + ylab("posterior probability")

# Kristian:
ggplot(d.3k, aes(grid, posterior.3k)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior.3/dens), colour='red') + xlab("Knowledge of CogSci - prior.3 Kristian") + ylab("posterior probability")

# Daina:
ggplot(d.3d, aes(grid, posterior.3d)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior.3/dens), colour='red') + xlab("Knowledge of CogSci - prior.3 Daina") + ylab("posterior probability")

# Mikkel:
ggplot(d.3m, aes(grid, posterior.3m)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior.3/dens), colour='red') + xlab("Knowledge of CogSci - prior.3 Mikkel") + ylab("posterior probability")
```
4. You go back to your teachers and collect more data (multiply the previous numbers by 100). Calculate their knowledge with both a uniform prior and a normal prior with a mean of 0.8 and a standard deviation of 0.2. Do you still see a difference between the results? Why?

This is the new data:
- Riccardo: 300 correct answers out of 600 questions
- Kristian: 200 correct answers out of 200 questions (then he gets bored)
- Daina: 16000 correct answers out of 19800 questions (Daina never gets bored)
- Mikkel: 6600 correct answers out of 13200 questions
```{r}
# Riccardo: 
# define the prior
R1prior <- rep(1, dens) # flat
R2prior <- dnorm(p_grid, 0.8, 0.2)

# Test the prior
dens(rbinom(1e4, 600, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
Rlikelihood <- dbinom(300, size = 600, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
R1unstd.posterior <- Rlikelihood * R1prior
R2unstd.posterior <- Rlikelihood * R2prior
# Standardize the posterior (so it sums to 1)
R1posterior <- R1unstd.posterior/sum(R1unstd.posterior)
R2posterior <- R2unstd.posterior/sum(R2unstd.posterior)


# make dataframes to draw plots 
R1d <- data.frame(grid= p_grid, posterior = R1posterior, prior = R1prior, likelihood = Rlikelihood)

R2d <- data.frame(grid= p_grid, posterior = R2posterior, prior = R2prior, likelihood = Rlikelihood)
# Draw plot
ggplot(R1d, aes(grid, R1posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, R1prior/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")

ggplot(R2d, aes(grid, R2posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, R2prior/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")


# Kristian

# define the prior
prior1 <- rep(1, dens) # flat
prior2 <- dnorm(p_grid, 0.8, 0.2)

# Test the prior
dens(rbinom(1e4, 200, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
Klikelihood <- dbinom(200, size = 200, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
K1unstd.posterior <- Klikelihood * prior1
K2unstd.posterior <- Klikelihood * prior2
# Standardize the posterior (so it sums to 1)
K1posterior <- K1unstd.posterior/sum(K1unstd.posterior)
K2posterior <- K2unstd.posterior/sum(K2unstd.posterior)


# make dataframes to draw plots 
K1d <- data.frame(grid= p_grid, posterior = K1posterior, prior = prior1, likelihood = Klikelihood)

K2d <- data.frame(grid= p_grid, posterior = K2posterior, prior = prior2, likelihood = Klikelihood)
# Draw plot
ggplot(K1d, aes(grid, K1posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior1/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")

ggplot(K2d, aes(grid, K2posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior2/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")


# Daina


# Test the prior
dens(rbinom(1e4, 19800, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
Dlikelihood <- dbinom(16000, size = 19800, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
D1unstd.posterior <- Dlikelihood * prior1
D2unstd.posterior <- Dlikelihood * prior2
# Standardize the posterior (so it sums to 1)
D1posterior <- D1unstd.posterior/sum(D1unstd.posterior)
D2posterior <- D2unstd.posterior/sum(D2unstd.posterior)


# make dataframes to draw plots 
D1d <- data.frame(grid= p_grid, posterior = D1posterior, prior = prior1, likelihood = Dlikelihood)

D2d <- data.frame(grid= p_grid, posterior = D2posterior, prior = prior2, likelihood = Dlikelihood)
# Draw plot
ggplot(D1d, aes(grid, D1posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior1/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")

ggplot(D2d, aes(grid, D2posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior2/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")


# Mikkel
# Test the prior
dens(rbinom(1e4, 13200, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
Mlikelihood <- dbinom(6600, size = 13200, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
M1unstd.posterior <- Mlikelihood * prior1
M2unstd.posterior <- Mlikelihood * prior2
# Standardize the posterior (so it sums to 1)
M1posterior <- M1unstd.posterior/sum(M1unstd.posterior)
M2posterior <- M2unstd.posterior/sum(M2unstd.posterior)


# make dataframes to draw plots 
M1d <- data.frame(grid= p_grid, posterior = M1posterior, prior = prior1, likelihood = Mlikelihood)

M2d <- data.frame(grid= p_grid, posterior = M2posterior, prior = prior2, likelihood = Mlikelihood)
# Draw plot
ggplot(M1d, aes(grid, M1posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior1/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")

ggplot(M2d, aes(grid, M2posterior)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior2/dens), colour='red') + xlab("Knowledge of CogSci") + ylab("posterior probability")

```


5. Imagine you're a skeptic and think your teachers do not know anything about CogSci, given the content of their classes. How would you operationalize that belief?

```{r}
# I would make the prior a normal distribution with a lower mean (0.65) and SD of 0.05. This would keep the prior to be low below 0.5 on the grid and above 0.75 on the grid.

# Testing this on Riccardo's data multiplied with 100.

# define the prior
prior5 <- dnorm(p_grid, 0.65, 0.05) 

# Test the prior
dens(rbinom(1e4, 600, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
likelihood <- dbinom(300, size = 600, prob = p_grid)
# 6 is the number of correct asnwers, 9 is the number of questions asked

# Compute the posterior (unstd = unstandardized)
unstd.posterior5 <- likelihood * prior5

# Standardize the posterior (so it sums to 1)
posterior5 <- unstd.posterior5/sum(unstd.posterior5)

# make dataframes to draw plots 
d5 <- data.frame(grid= p_grid, posterior = posterior5, prior = prior5, likelihood = likelihood)

# Draw plot
ggplot(d5, aes(grid, posterior5)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior5/dens), colour='red') + xlab("Knowledge of CogSci - Riccardo / Skeptic prior") + ylab("posterior probability")


```


6. Optional question: Can you estimate the difference between Riccardo's estimated knowledge and that of each of the other teachers? Would you deem it credible (that is, would you believe that it is actually different)? 

### Second part: Focusing on predictions

Last year you assessed the teachers (darned time runs quick!). Now you want to re-test them and assess whether your models are producing reliable predictions. In Methods 3 we learned how to do machine-learning style assessment of predictions (e.g. rmse on testing datasets). Bayesian stats makes things a bit more complicated. So we'll try out how that works. N.B. You can choose which prior to use for the analysis of last year's data.

Questions to be answered (but see guidance below):
1- Write a paragraph discussing how assessment of prediction performance is different in Bayesian vs. frequentist modle:

:   In Bayesian models, we update our prior belief with evidence and calculate a posterior belief.

: In frequentist model we only take the probability of something without using the prior knowledge we have.

In this way, Bayesian models are always generative, capable of simulating predictions. Many non-Bayesian models are also generative, but many are not. (for assignment 1, part 2).

In frequentist models we can use t-tests to get a p-value which indicates whether or not the means are significantly different. Whereas bayesian models estimate how likely it is the model has learned something. The Bayesian model is more flexible (you can change the parameters, modify the models and crossreference it. We can update our model with the new information we have.) and learns using the information we have. Bayesian models can use simulations to learn and to check the validity of the model. If we have new data, we can calculate a new posterior using the previous posterior as a prior. 



2- Provide at least one plot and one written line discussing prediction errors for each of the teachers.

This is the old data:
- Riccardo: 3 correct answers out of 6 questions
- Kristian: 2 correct answers out of 2 questions (then he gets bored)
- Daina: 160 correct answers out of 198 questions (Daina never gets bored)
- Mikkel: 66 correct answers out of 132 questions

This is the new data:
- Riccardo: 9 correct answers out of 10 questions (then he freaks out about teaching preparation and leaves)
- Kristian: 8 correct answers out of 12 questions
- Daina: 148 correct answers out of 172 questions (again, Daina never gets bored)
- Mikkel: 34 correct answers out of 65 questions

( We are using the old model to predict and I am supposed to calculate the difference/error of the model and the actual data)

Guidance Tips

1. There are at least two ways of assessing predictions.
2. Last year's results are this year's expectations.
3. Are the parameter estimates changing? (way 1)
4. How does the new data look in last year's predictive posterior? (way 2)


```{r}

# Use the posteriors from the earlier questions as priors. Calculate the difference between the posterior of the old data and the posterior of the new data.


# We use the posteriors of the old data (from question 3) as priors for the new data.
prior_newR <- posterior.3
prior_newK <- posterior.3k
prior_newD <- posterior.3d
prior_newM <- posterior.3m

# Test the priors
dens(rbinom(1e4, 10, runif(1e4, 0,1)))
dens(rbinom(1e4, 12, runif(1e4, 0,1)))
dens(rbinom(1e4, 172, runif(1e4, 0,1)))
dens(rbinom(1e4, 65, runif(1e4, 0,1)))

# Compute the likelihood at each value in the grid 
likelihood_newR <- dbinom(9, size = 10, prob = p_grid)
likelihood_newK <- dbinom(8, size = 12, prob = p_grid)
likelihood_newD <- dbinom(148, size = 172, prob = p_grid)
likelihood_newM <- dbinom(34, size = 65, prob = p_grid)

# Compute the posterior (unstd = unstandardized)
unstd.posterior_newR <- likelihood_newR * prior_newR
unstd.posterior_newK <- likelihood_newK * prior_newK
unstd.posterior_newD <- likelihood_newD * prior_newD
unstd.posterior_newM <- likelihood_newM * prior_newM

# Standardize the posterior (so it sums to 1)
posterior_newR <- unstd.posterior_newR/sum(unstd.posterior_newR)
posterior_newK <- unstd.posterior_newK/sum(unstd.posterior_newK)
posterior_newD <- unstd.posterior_newD/sum(unstd.posterior_newD)
posterior_newM <- unstd.posterior_newM/sum(unstd.posterior_newM)


# make dataframes to draw plots 
d_newR <- data.frame(grid= p_grid, posterior = posterior_newR, prior = prior_newR, likelihood = likelihood_newR)
d_newK <- data.frame(grid= p_grid, posterior = posterior_newK, prior = prior_newK, likelihood = likelihood_newK)
d_newD <- data.frame(grid= p_grid, posterior = posterior_newD, prior = prior_newD, likelihood = likelihood_newD)
d_newM <- data.frame(grid= p_grid, posterior = posterior_newM, prior = prior_newM, likelihood = likelihood_newM)

# Plot
ggplot(d_newR, aes(grid, posterior_newR)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior_newR/dens), colour='red') + xlab("Knowledge of CogSci - Riccardo updated") + ylab("posterior probability")

ggplot(d_newK, aes(grid, posterior_newK)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior_newK/dens), colour='red') + xlab("Knowledge of CogSci - Kristian updated") + ylab("posterior probability")

ggplot(d_newD, aes(grid, posterior_newD)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior_newD/dens), colour='red') + xlab("Knowledge of CogSci - Daina updated") + ylab("posterior probability")

ggplot(d_newM, aes(grid, posterior_newM)) + geom_point() + geom_line() + theme_classic() + geom_line(aes(grid, prior_newM/dens), colour='red') + xlab("Knowledge of CogSci - Mikkel updated") + ylab("posterior probability")


```

## Posterior predictions - sampling from posterior distribution to create predictions.

```{r}



# Create an object named samples_XX (because this function samples) <- specify dataframe that contains the posterior distribution you want to use - pipes - 'dplyr::slice_sample()' samples - specify the amount of samples you want, "weight_by= posterior" - we want it the sample proportionate to the posterior distribution. "replace = TRUE" - just because.

samples_ric <- d_newR %>% 
  dplyr::slice_sample(n = 1e4, weight_by = posterior, replace = TRUE)
# Samples of the parameter (weighted_by= posterior (i.e taking more samples from where the posterior density is tall - proportional to the posterior density))

samples_kri <- d_newK %>%
  dplyr::slice_sample(n = 1e4, weight_by = posterior, replace = TRUE)

samples_dai <- d_newD %>%
  dplyr::slice_sample(n = 1e4, weight_by = posterior, replace = TRUE)

samples_mik <- d_newM %>%
  dplyr::slice_sample(n = 1e4, weight_by = posterior, replace = TRUE)

# Extract the mean and standard deviation (SD) of the grid in the samples_object. 
mean(samples_ric$grid)
sd(samples_ric$grid)

mean(samples_kri$grid)
sd(samples_dai$grid)

mean(samples_dai$grid)
sd(samples_dai$grid)

mean(samples_mik$grid)
sd(samples_mik$grid)
```
 
```{r}
# create an object with a name - make a tibble (you can also make dataframe) - writing "predictions=" before rbinom() names the sample column 'predictions' - we want it to sample from the posterior distribution (with the same proportions as the posterior distributions) - rbinom() - takes n samples. "size = 10" - how many questions were asked. "prob = rnorm(sample amount, mean, SD) - mean and SD were extracted above.
predictive_post_R <- tibble(predictions = rbinom( n = 1e4, size = 10, prob= rnorm( 1e4, 0.741, 0.088))) %>%
  filter(!is.na(predictions)) #Remove NA's

predictive_post_K <- tibble(predictions = rbinom( n = 1e4, size = 12, prob= rnorm( 1e4, 0.718, 0.017))) %>%
  filter(!is.na(predictions)) #Remove NA's

predictive_post_D <- tibble(predictions = rbinom( n = 1e4, size = 148, prob= rnorm( 1e4, 0.836, 0.017))) %>%
  filter(!is.na(predictions)) #Remove NA's

predictive_post_M <- tibble(predictions = rbinom( n = 1e4, size = 34, prob= rnorm( 1e4, 0.516, 0.034))) %>%
  filter(!is.na(predictions)) #Remove NA's

# Making histogram (this only needs the x-axis)
ggplot(predictive_post_R, aes(x = predictions)) + geom_histogram() + xlab("Predictions Riccardo")

ggplot(predictive_post_K, aes(x = predictions)) + geom_histogram() + xlab("Predictions Kristian")

ggplot(predictive_post_D, aes(x = predictions)) + geom_histogram() + xlab("Predictions Daina")

ggplot(predictive_post_M, aes(x = predictions)) + geom_histogram() + xlab("Predictions Mikkel")


```
 
```{r}

```


```{r}

```

